### 2024-08-23 paper.tex
something
no lie group

\subsection{Springer fibers}
Let \(G \subseteq \GL_m\) be a connected semisimple Lie group, and let \(\mathfrak{g} \subseteq \gl_m\) be its Lie algebra.
(TODO: either say something interesting about the Lie group, or just get rid of it and talk only about the Lie algebra.)
% ^I take this scope because it is about what Yuzhou Gu said.
Let \(\mathcal{N} \subseteq \mathfrak{g}\) be the subset consisting of nilpotent elements.
Let \(\mathcal{B}\) be the variety of Borel subalgebras of \(\mathfrak{g}\).
Let \(\widetilde{\mathcal{N}} = \{(\mathfrak{b}, n) : n \in \mathfrak{b}\} \subseteq \mathcal{B} \times \mathcal{N}\).
Let \(\pi : \widetilde{\mathcal{N}} \to \mathcal{N}\) be the projection onto the second coordinate.
We call this the \emph{Springer resolution}.
For \(n \in \mathcal{N}\), we call \(\pi^{-1}(n)\) the \emph{Springer fiber at \(n\)}.

@@

\par First, we provide an alternative characterization of \(B_{I, (\rho_i)}\).
Let \(B_{I, (\rho_i)}'\) be the set of \(b \in \mathbb{C}^m\) satisfying the following conditions.
\begin{itemize}
    \item For all \(k \in \{1, ..., r\}\), \(p_i = \rho_i\).
    \item For \(i \notin I\), let \(S = \{k \in \{1, ..., r + 1\} : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
    If \(S = \emptyset\), then \(p_i \leq \lambda_i - q_{i_0}\).
    If \(r + 1 \in S\), then \(p_i \leq p_{i_{r + 1}}\).
    Otherwise, \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\), where \(k = \max S\).\footnote{I could remove the edge cases if I define \(q_{i_{-1}}\) and \(q_{i_{r + 1}}\)... ah, maybe a bit less drastically, I can say something like min(complement of S) instead of max(S)}
\end{itemize}
\begin{lemma}\label{alternative_bs}
    \(B_{I, (\rho_i)} = B_{I, (\rho_i)}'\).
\end{lemma}
\begin{proof}
    First we show that \(B_{I, (\rho_i)} \subseteq B_{I, (\rho_i)}'\).
    Let \(b \in B_{I, (\rho_i)}\).
    It is clear that \(\forall i \in I. \; p_i = \rho_i\).
    \par First suppose \(S = \emptyset\).
    Then if we had \(q_i < q_{i_0}\), this would entail \(p_i \leq \max_{j : q_j < q_{i_0}} = p_{i_1}\).
    But then \(\lambda_i = p_i + q_i < q_{i_0} + p_{i_1}\), contradicting that \(1 \notin S\).
    Hence \(q_i \geq q_{i_0}\), and therefore \(p_i \leq \lambda_i - q_{i_0}\).
    \par Now suppose \(r + 1 \in S\).
    Then \(q_{i_r} = q_{i_r} + p_{i_{r + 1}} > \lambda_i\).
    Then certainly \(q_i < q_{i_r}\), and therefore \(p_i \leq \max_{j : q_j < q_{i_r}} p_j = p_{i_{r + 1}}\).
    \par If we are in neither of those cases, let \(k = \max S\).
    We have \(q_{i_k} + p_{i_{k + 1}} \leq \lambda_i\).
    Suppose we had \(q_i < q_{i_k}\).
    Then \(p_i \leq \max_{j : q_j < q_{i_k}} p_j = p_{i_{k + 1}}\).
    But then \(p_i + q_i < q_{i_k} + p_{i_{k + 1}} \leq \lambda_i\), which is a contradiction since \(k + 1 \notin S\).
    Thus \(q_i \geq q_{i_k}\).
    Now, we have two cases: either \(q_i \geq q_{i_{k - 1}}\), or \(q_i < q_{i_{k - 1}}\).
    In the second case, we see that \(p_i \leq p_{i_k}\).
    In the first, recall we also have \(q_{i_{k - 1}} + p_{i_k} > \lambda_i = p_i + q_i\) (since \(k \in S\)), so \(p_{i_k} > p_i\).
    So, in any case, we have \(q_i \geq q_{i_k}\) and \(p_i \leq p_{i_k}\); or, in other words, \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\).
    \par Hence \(b \in B'_{I, (\rho_i)}\), and we see that \(B_{I, (\rho_i)} \subseteq B'_{I, (\rho_i)}\).
    Now we show the opposite inclusion.
    Let \(b \in B_{I, (\rho_i)}\).
    Again it is clear that \(\forall i \in I. \; p_i = \rho_i\).
    \par Let \(k \in \{0, ..., r\}\).
    I need to show that \(p_{i_{k + 1}} = \max_{j : q_j < q_{i_k}} p_j\).
    It suffices to show that for every \(i \in I\), either \(p_i \leq p_{i_{k + 1}}\) or \(q_i \geq q_{i_k}\).
    Agh.  continue here.
\end{proof}

\begin{corollary}\label{bs_iso}
    \[B_{I, (\rho_i)} \cong \prod_{i \in I} \mathbb{C}^{blah} \times \prod_{i \notin I}\]
\end{corollary}

>>>>

\subsection{Springer fibers}
Let \(\mathfrak{g}\) be a Lie algebra.
Let \(\mathcal{N} \subseteq \mathfrak{g}\) be the subset consisting of nilpotent elements.
Let \(\mathcal{B}\) be the variety of Borel subalgebras of \(\mathfrak{g}\).
Let \(\widetilde{\mathcal{N}} = \{(\mathfrak{b}, n) : n \in \mathfrak{b}\} \subseteq \mathcal{B} \times \mathcal{N}\).
Let \(\pi : \widetilde{\mathcal{N}} \to \mathcal{N}\) be the projection onto the second coordinate.
We call this the \emph{Springer resolution}.
For \(n \in \mathcal{N}\), we call \(\pi^{-1}(n)\) the \emph{Springer fiber at \(n\)}.

@@

\par First, we provide an alternative characterization of \(B_{I, (\rho_i)}\).
Let \(B_{I, (\rho_i)}'\) be the set of \(b \in \mathbb{C}^m\) satisfying the following conditions.
\begin{itemize}
    \item For all \(k \in \{1, ..., r\}\), \(p_i = \rho_i\).
    \item For \(i \notin I\), let \(S = \{k \in \{1, ..., r + 1\} : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
    If \(S = \emptyset\), then \(p_i \leq \lambda_i - q_{i_0}\).
    If \(r + 1 \in S\), then \(p_i \leq p_{i_{r + 1}}\).
    Otherwise, \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\), where \(k = \max S\).\footnote{I could remove the edge cases if I define \(q_{i_{-1}}\) and \(q_{i_{r + 1}}\)... ah, maybe a bit less drastically, I can say something like min(complement of S) instead of max(S)}
\end{itemize}
\begin{lemma}\label{alternative_bs}
    \(B_{I, (\rho_i)} = B_{I, (\rho_i)}'\).
\end{lemma}
\begin{proof}
    First we show that \(B_{I, (\rho_i)} \subseteq B_{I, (\rho_i)}'\).
    Let \(b \in B_{I, (\rho_i)}\).
    It is clear that \(\forall i \in I. \; p_i = \rho_i\).
    \par First suppose \(S = \emptyset\).
    Then if we had \(q_i < q_{i_0}\), this would entail \(p_i \leq \max_{j : q_j < q_{i_0}} = p_{i_1}\).
    But then \(\lambda_i = p_i + q_i < q_{i_0} + p_{i_1}\), contradicting that \(1 \notin S\).
    Hence \(q_i \geq q_{i_0}\), and therefore \(p_i \leq \lambda_i - q_{i_0}\).
    \par Now suppose \(r + 1 \in S\).
    Then \(q_{i_r} = q_{i_r} + p_{i_{r + 1}} > \lambda_i\).
    Then certainly \(q_i < q_{i_r}\), and therefore \(p_i \leq \max_{j : q_j < q_{i_r}} p_j = p_{i_{r + 1}}\).
    \par If we are in neither of those cases, let \(k = \max S\).
    We have \(q_{i_k} + p_{i_{k + 1}} \leq \lambda_i\).
    Suppose we had \(q_i < q_{i_k}\).
    Then \(p_i \leq \max_{j : q_j < q_{i_k}} p_j = p_{i_{k + 1}}\).
    But then \(p_i + q_i < q_{i_k} + p_{i_{k + 1}} \leq \lambda_i\), which is a contradiction since \(k + 1 \notin S\).
    Thus \(q_i \geq q_{i_k}\).
    Now, we have two cases: either \(q_i \geq q_{i_{k - 1}}\), or \(q_i < q_{i_{k - 1}}\).
    In the second case, we see that \(p_i \leq p_{i_k}\).
    In the first, recall we also have \(q_{i_{k - 1}} + p_{i_k} > \lambda_i = p_i + q_i\) (since \(k \in S\)), so \(p_{i_k} > p_i\).
    So, in any case, we have \(q_i \geq q_{i_k}\) and \(p_i \leq p_{i_k}\); or, in other words, \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\).
    \par Hence \(b \in B'_{I, (\rho_i)}\), and we see that \(B_{I, (\rho_i)} \subseteq B'_{I, (\rho_i)}\).
    Now we show the opposite inclusion.
    Let \(b \in B_{I, (\rho_i)}\).
    Again it is clear that \(\forall i \in I. \; p_i = \rho_i\).
    \par Let \(k \in \{0, ..., r\}\).
    I need to show that \(p_{i_{k + 1}} = \max_{j : q_j < q_{i_k}} p_j\).
    It suffices to show that for every \(i \in I\), either \(p_i \leq p_{i_{k + 1}}\) or \(q_i \geq q_{i_k}\).
    First suppose \(k + 1 \in S_i\).
    Then \(p_i \leq p_{i_{k + 1}}\), by definition of \(S_i\)... (not directly, but basically).
    Now suppose \(k + 1 \notin S_i\).
    Then \(q_i \geq ... (something) ... \geq q_{i_k}\).
\end{proof}

\begin{corollary}\label{bs_iso}
    \[B_{I, (\rho_i)} \cong \prod_{k = 1}^r \mathbb{C}^{\rho_{i_k}} \times \prod_{i \geq q_{i_0}} \mathbb{C}^{\lambda_i - n} \times \prod_{k = 0}^r \prod_{}\mathbb{C}^{}\]
\end{corollary}
